Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language

### 2019-01-13 Publication/tex_manuscript/manuscript.tex
tex code formatting

%Document Head
\dochead{CLV3 Class File Manual}

\runningtitle{How to Use CLV3 \LaTeX\ Class File}

\runningauthor{Odi\'e N. Gementera}

@@

\title{How to Use CLV3 \LaTeX\ Class File}

\author{Odi\'e N. Gementera\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
\affil{Publishing / SPi}

@@

This document applies to version 3 of CL class file. Prior style files such as 
``{\tt cl.sty}'' and ``{\tt coli.sty}'' do not have all of the features 
described here. It is assumed that the user has a basic knowledge of \LaTeX\ 
typesetting commands.

\section{Class File Options}

There are several options that can be used to switch the mode of MIT2 from normal 
article to manuscript style, or to different layout styles. This is specified in 
the usual \LaTeX\ way by declaring:

@@

\section{Title Page}

>>>>

%Document Head
\dochead{Journal of Computational Linguistics}

\runningtitle{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}

\runningauthor{Russell J. Jarvis}

@@

\title{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}

\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
\affil{Publishing / SPi}

@@

Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed using a lower complexity and more engaging writing style.  However, multiple stake holders could benefit if science was more often communicated using a lower complexity expression of ideas. Knowledge would be more readily mobilized and transferred into public awareness, also, and machine readability and machine organization of factual information derived from journal articles should also occur more readily.

We believe non-science writing occupies a style niche, that academic science writing should also occupy. We show that we can blindly predict the status of writing: popular culture writing, opinionative writing, and traditional science, by using machine learning to classify the different writing types. By predicting which of the several different writing types any writing piece occupies, we are able to characterize among different writing niches.

Objectively describing the different character of the different writing styles will allow us to prescribe how, to shift academic science writing into a more accessible niche, where science can more aggressively compete with pseudo-science, and blogs, facilitating greater knowledge transference, at a moment in history when public awareness is critically at stake.

\section{Methods}

We built a web-scraping and written text analysis infrastructure by extending many existing Free and Open Source (FOS) tools. The Web scrapping interface employs several common python modules, chief among those was: Google Scrape, Beautiful Soup and Selenium. The Text analysis infrastructure was based on the two substantial code bases Text-stat, which contained measures of text reading level (complexity), and NLTK (the Natural Language Processing Tool Kit), which contained measures of text subjectivity, and sentiment type.

The scraping, and analysis work we performed, rested on top of a large hierarchy of software dependencies. However, it is increasingly well understood, that, dependency heavy software stacks act as a significant impediment to investigating or reproducing any product of digital, scholary research. In order to address this problem and to enhance the reproducibility of our approach, we created the necessary web-scrapping, and analysis infrastructure inside a dedicated Docker Container.

Reproducibility is burdened by the technical task of satisfying each software dependencies necessary to recreate a digital scientific experiment. Our position, of starting with from a cloned software environment, will mitigate, the burden of duplicating our digital research environment. That is why we have used a Docker file, and associated Docker container together, as they act as self-documenting and extremely portable software environment clone.

Initially we created two different, unrelated and broad ranging lists of scientific queries. The first type of query was predominantly cultural in nature, or world view related. The second set of queries represented gains in knowledge about physical entities or physical processes in the world. We were interested in scientific, and pseudo-scientific writing.

There were two types of writing that we actively excluded from our analysis, those were websites expressed in a non-English language, and also websites, that were highly commercial in nature. These were websites advertisements, of consumer goods, and online shopping generally. These websites, utilizing wording, that significantly biases text stat metrics. Webpages of less than 400 words, were most often advertisements, and websites
Non English, websites were excluded for the simple reason that they are not amenable to Textstat, and NLTK tools, however, even if this was not the case, it is also known, that there are  significant differences in per-word information entropy between different natural languages.

\subsection{Search Engine Queries:}
The first two lists of queries were chosen to be belong to an overt set of exclusively scientific or cultural search terms. A third list of terms was designed to be deliberately ambiguous.

\subsection{Science Queries:}
The three lists of search engine queries were as implemented as follows: science engine queries: 'evolution', 'photo-sysnthesis' ,'Transgenic', 'GMO', 'climate change', 'cancer', 'Vaccines', 'Genetically Modified Organism', ‘differential equation’,"psycho-physics","soma”

Cultural queries were as follows: 'reality TV', 'prancercise philosophy', 'play dough delicious deserts', 'unicorn versus brumby', 'football soccer' , god fearing.

As discussed we also designed ambiguous queries which were equally likely return content that was either scientific, or non scientific in nature. The reason for doing this was to provide a challenge for the classification algorithm.

\subsection{Ambiguous Queries, were as follows:}

"the singularity","skynet","","killer robot","franken-science","Frankenstein,”the God Delusion","god does not play dice", "the selfish gene","political science", ", "requim for a spike"

After scraping across the two different lists were performed, the resulting queries were filtered, according to specific sets of criteria. As stated previously, we discarded from our analysis, web pages that were not written in English, since we did not have the necessary tools, to analyze them.

Text Metrics:
A list of metrics applied to downloaded corpus include: TextStat, which was used to measure word complexity (an average of several important word complexity metrics, such as the Gunning Fog measure of reading level), LZW compression-ratio, de-compression ratio, sentiment analysis, subjectivity analysis, and page rank.

Compression ratios were used to investigate the notion, that well written scientific writing, might simply be lower in information entropy, and an information theoretic analysis, can be used to both to better characterize, and corroborate the findings of other reading word complexity metrics

\subsection{Reference Texts:}

Some reference texts were used, as a means of providing contrast, and context, to data points, among our web scraping derived corpus. The Upgoer5 is a library, of scientific texts, written with the aid of a text editor, which imposes, that output documents are exclusively comprised by, only the 10,000 most commonly occurring English words.

The Post Modern Essay Generator (PMEG), embodies an artificial English synthesis technique. Documents that are output from the website, consist of sentences that obey the rules of written English, however there are no restraints governing the semantic conceptual references in the sentences. If any particular sentence in a PMEG document, embodies an objective meaning, it is only by chance. Output from PMEG reads as highly coded, and vague.

The reference data points in some ways provide further validation to the existing text metric tools, as we needed to verify that word readability metrics provided results that were consistant with prior assumptions about known texts. For instance, the corpus derived from upgoer editor, should require a very low reading grade level to understand. Texts, from the PMEG should require a very high reading level to understand, and cumulative entropy of such texts should be high.

@@

\section{Results}
